---
title: "LIMA_SA2_NUMBER26"
output: html_document
date: "2023-12-17"
---
## Dataset Description

The effect of two-dimensional visual stimuli on rats' spontaneous exploring activity caught the curiosity of a cognitive psychologist.   Thirty-six (n = 36) rats were chosen for the experiment and divided into three groups at random for treatment:

**Visual images of shapes**
**Visual images of patterns**
**Visual images that used pictures**

Rats were released into a chamber and the number of seconds the rats spent exploring the experimental chamber with the images were recorded.

### Checking of Assumptions

**Assumption #1:**

The dependent variable, time or time_exploration, is measured at the continuous level.

**Assumption #2:**
The independent variable, stimuli or visual_stimuli consists of three categorical groups: shape, pattern, picture.

**Assumption #3:**
Since there is no relationship between the observations in each group of the independent variable or between the groups themselves, each observation is independent of the others.

**Assumption #4:**
There are no significant outliers found in the visual stimuli groups of the labrats in terms of time_exploration, as assessed by visual inspection of boxplots

```{r boxplot, echo=FALSE}
library(tidyverse)
library(rstatix)
library(car)
library(ggplot2)
library(lme4)
library(dplyr)

data_labrats <- data.frame(
  visual_stimuli = c("Shape", "Shape", "Shape", "Shape", "Shape", "Shape", "Shape", "Shape",
                  "Pattern", "Pattern", "Pattern", "Pattern", "Pattern", "Pattern", "Pattern", "Pattern",
                  "Picture", "Picture", "Picture", "Picture", "Picture", "Picture", "Picture", "Picture",
                  "Shape", "Shape", "Shape", "Shape", "Pattern", "Pattern", "Pattern", "Pattern",
                  "Picture", "Picture", "Picture", "Picture"),
  time_exploration = c(2,0.75,1.25,1,1.5,1.25,1.75,0.5,2.5,3.25,1.85,3.05,2.5,3,4.1,3.75,4.25,4.1,4.25,4.4,3.75,3.05,3.2,5,2,0.75,1.25,1,2.5,3.25,1.85,3.05,4.25,4.4,3.75,3.05)
)

# Box plot
boxplot(time_exploration ~ visual_stimuli, data = data_labrats, col = "cyan", border = "black",
        main = "Boxplot of Time Exploration by Visual Stimuli",
        xlab = "Visual Stimuli", ylab = "Time Exploration",
        outline = TRUE) 

```

**Assumption #5:**
The time_exploration is approximately normally distributed for each of the physical activity groups, as assessed by Shapiro-Wilk's test, p > 0.05.

```{r shapiro, echo=FALSE}

# Shapiro-Wilk test for normality 
shapiro_test <- data_labrats %>%
  group_by(visual_stimuli) %>%
  summarise(p_value = shapiro.test(time_exploration)$p.value)

# Print result
print("SHAPIRO-WILK's Test:")
print(shapiro_test)

```


**Assumption #6:**
There was homogeneity of variances of the dependent variable for all physical activity groups, as assessed by Levene's test of homogeneity of variances, p = 0.653

```{r levene, echo=FALSE}

# Levene's test for homogeneity of variances
levene_test <- car::leveneTest(time_exploration ~ visual_stimuli, data = data_labrats)
print("LEVENE's Test:")
print(levene_test)

```

### COMPUTATION
```{r computation, echo=FALSE}

# ANOVA - time_exploration
ANOVA <- aov(time_exploration ~ visual_stimuli, data = data_labrats)
summary(ANOVA)

# Descriptive statistics
descriptiveStats <- data_labrats %>%
  group_by(visual_stimuli) %>%
  summarise(
    mean_time = mean(time_exploration),
    sd_time = sd(time_exploration),
    n = n()
  )
print("Descriptive Statistics:")
print(descriptiveStats)

# POST-HOC TEST
posthoc <- data_labrats %>%
  tukey_hsd(time_exploration ~ visual_stimuli)

print("POST-HOC Test:")
print(posthoc)
```

**Report:**

The statistical significance of the changes in mileage of five cars using four different oils was assessed using a one-way ANOVA. According to the boxplot there were no outlier. In the shapiro-wilk test the p values for each visual_stimuli category/group are all above 0.05 and levene's test show that the p-value is 0.653 > 0.05, therefore there is no evidence to reject the null hypothesis for any group.The one-way ANOVA test indicates a significant difference in the mean time exploration accross different visual stimuli conditions. Post-hoc revealed that there is significant differences in mean time exploration between Pattern and Picture, Pattern and Shape, and Picture and shape. Hence we can statistically conclude that there is a significant impact of 2 - dimensional visual stimuli on the spontaneous exploration behavior in rats.
